Academic Advancement Advice: Author Articles as A.~A.

### 2018-03-15 trunk/citations/paper.tex
More work on paper, clean up titles

@@

% 78371002.  5.3718855409784041e-027	53e9a089b7602d970296e0eb	Office Hours: Monday, Wednesday, Thursday and Friday 9:00 a.m. to 5:00 p.m.; Tuesday 9:00 a.m. to 6:45 p.m

% 78370998.  6.049184011159267e-027	56d81919dabfae2eee86f82a	Thomas Aquinas: Theologian By Thomas F. O'Meara, O.P. Notre Dame, University of Notre Dame Press, 1997. 302 pp. $16.95

The first is probably not the title of an article, although we can
agree that it is unlikely to be cited. The second is a bad entry, with
the entire citation packed into the title field. This book actually
does have 94 citations (or DOES IT?~\cite{o1997thomas}) on Google
Scholar and an Amazon Sales Rank of \#10,837 in {\em Christian
  Denominations \& Sects}. In order to prevent such data problems from
affecting our results, I then added a requirement that the article
have basic metadata (either a Digital DOI Identifier field or {\tt venue})
for it to be considered.

% 48654527.  5.8084026066881388e-026	56d918ecdabfae2eee6c6965	Eight contemporary poets : Charles Tomlinson, Donald Davie, R.S. Thomas, Philip Larkin, Ted Hughes, Thomas Kinsella, Stevie Smith, W.S. Graham

@@

1. memorials for dead guys
2. reviews of books
3. articles not in english
4. broken citations

\largeskip
Of course, since these papers are all notable for being so extremely
uncitable, the true least citable papers are the next least citable,
according to this analysis.

@@

Adopting an all-'A' affect also advances articles. Although affairs
are abbreviated, adequate abstracts abound: Astronomy, asthma,
atmospheric acclimatization, autobiography, Azerbaijani accents,
acceleration, and abundant alternatives.

@@

Awesome!

@@

>>>>

\def\signed#1{{\unskip\nobreak\hfil\penalty50
    \hskip2em\hbox{}\nobreak\hfil\sl#1
    \parfillskip=0pt \finalhyphendemerits=0 \par}}

@@

\begin{quote}
 Office Hours: Monday, Wednesday, Thursday and Friday 9:00 a.m. to 5:00 p.m.; Tuesday 9:00 a.m. to 6:45 p.m \\
  \signed{(citation multiplier $5.37\!\times\!10^{-27}$)}
\end{quote}

\begin{quote}
	Thomas Aquinas: Theologian By Thomas F. O'Meara, O.P. Notre Dame, University of Notre Dame Press, 1997. 302 pp. \$16.95 \\
  \signed{(citation multiplier $6.05\!\times\!10^{-27}$)}
\end{quote}

The first is probably not the title of an article\cite{officehours},
although we can agree that it is unlikely to be cited. The second is
probably a bad entry, with the entire citation packed into the title
field. This book actually does have 94 citations (or DOES
IT?~\cite{o1997thomas}) on Google Scholar and an Amazon Sales Rank of
\#10,837 in {\em Christian Denominations \& Sects}.\footnote{ On the
  other hand, the entry does have a different
  author\cite{stevenson2000thomas}, so it could possibly be a review
  of this book whose title is literally the string above, including
  the price?} In order to prevent such data problems from affecting
our results, I then added a requirement that the article have basic
metadata (either a Digital DOI Identifier field or {\tt venue}) for it
to be considered. There are still many broken entries, but picking through
the results I'm able to find what appear to be actual articles:

\begin{quote}
  % 48654527.  5.8084026066881388e-026	56d918ecdabfae2eee6c6965
  Eight contemporary poets : Charles Tomlinson, Donald Davie, R.S. Thomas, Philip Larkin, Ted Hughes, Thomas Kinsella, Stevie Smith, W.S. Graham
  \signed{(citation multiplier $5.8\!\times\!10^{-26}$)}
\end{quote}

@@

Lessons learned:
The least-cited works take the following typical forms. Acade
1. memorials for dead guys
2. reviews of books
3. articles not in english
4. broken citations

\medskip
Of course, since these papers are all notable for being so extremely
uncitable, the true least citable papers are the next least citable,
according to this analysis.

@@

Adopting an all-'A' affect also advances articles. Although affairs
are abbreviated, adequate abstracts abound: Astronomy, asthma,
atmospheric acclimatization, autobiography, Azerbaijani accents,
acceleration, and abundant alternatives. After achieving academic
accomplishments, acknowledge A.A.'s {\it Academic Advancement Advice:
  Author Articles as A.~A}!

@@

@@

\begin{verbatim}  
{"id": "56d8981adabfae2eee20314b", "title": "IMPLEMENTASI PERATURAN MAHKAMAH AGUNG NOMOR 1 TAHUN 2008 TENTANG PROSEDUR MEDIASI DI PENGADILAN (STUDI PUTUSAN MEDIASI DI PENGADILAN NEGERI SAMARINDA)", "authors": [{"name": "frianur ivan zairani lisi insan tajali nur"}], "year": 2013, "lang": "en"}
{"id": "56d8a690dabfae2eee9057b0", "title": "Pengaruh Pengawasan Inspektorat Dan Partisipasi Dalam Penyusunan Anggaran Terhadap Kinerja Manajerial SKPD (Studi Empiris Pada Instansi Pemerintah Kabupaten Tanah Datar)", "authors": [{"name": "retno nabila sari"}], "year": 2015, "lang": "en"}
{"id": "56d8ecc5dabfae2eee5b30f5", "title": "Narratives Unsettled: Digression in Robert Walser, Thomas Bernhard, and Adalbert Stifter by Samuel Frederick (review)", "authors": [{"name": "tove holmes"}], "venue": "Monatshefte", "year": 2015, "lang": "en"}
{"id": "56d918ecdabfae2eee6c6965", "title": "Eight contemporary poets : Charles Tomlinson, Donald Davie, R.S. Thomas, Philip Larkin, Ted Hughes, Thomas Kinsella, Stevie Smith, W.S. Graham", "authors": [{"name": "calvin bedient"}], "venue": "Modern Language Review", "year": 1975, "lang": "en"}
{"id": "56d9266ddabfae2eeebdd19a", "title": "Catherine Mowry LaCugna's Trinitarian Theology: III- The Ecumenical Implications of Catherine Mowry Lacugna's Trinitarian Theology", "authors": [{"name": "alan j torrance", "org": "university of st andrews"}], "venue": "Horizons", "year": 2000, "lang": "en", "doi": "10.1017/S036096690003262X", "url": ["http://dx.doi.org/10.1017/S036096690003262X"]}
{"id": "56d85cd0dabfae2eee5cb5f4", "title": "Texts Illustrating the Causality of the Sacraments from William of Melitona, Assisi Bibl. Comm. 182, and Brussels Bibl. Royale 1542", "authors": [{"name": "f o f m kilian lynch"}], "year": 1957, "lang": "en", "doi": "10.1353/frc.1957.0003", "url": ["http://dx.doi.org/10.1353/frc.1957.0003"]}
\end{verbatim}
